### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Final version

To answer these questions, we first start with
Figure~\ref{fig:perf_vs_dataset}, where we evaluate the performance of
various feature selection algorithms per dataset, averaged across
classifier type and each stage of feature selection. We can observe
here that our approaches generally perform well on recall (at a
reasonable accuracy level).  Notably, CVL performs best and
significantly better than competing methods on the NG and S datasets,
which we remark have the highest feature-to-data ratio and hence 
represent noisy cases for feature selection.  
%These results 
%indicate that the strong conjunctive voting scheme of CVL may help reduce 
%noise in feature selection for these datasets as previously conjectured.

@@

Next we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
performance distribution of various feature selection algorithms for
two datasets -- NG and S -- and classifier types -- Logistic
Regression and Naive Bayes -- at each stage of feature selection.
This graph shows that our CVL and CVE high recall feature selection
approaches provide strong recall performance at all stages of
feature selection in comparison to other selection methods.
%whose performance varies widely.
%We conjecture the reason for this stems from the strong agreement of
%features provided by the conjunctive voting scheme that helps reduce noise
%during feature selection process.

>>>>

To answer these questions, we first start with
Figure~\ref{fig:perf_vs_dataset}, where we evaluate the performance of
various feature selection algorithms per dataset, averaged across
classifier type and each stage of feature selection. We can observe
here that our approaches generally perform well on recall (at a
reasonable accuracy level).  Notably, CVL performs best and
significantly better than competing methods on the NG and S datasets,
which we remark have the highest feature to data ratio and hence 
represent noisy cases for feature selection.  
%These results 
%indicate that the strong conjunctive voting scheme of CVL may help reduce 
%noise in feature selection for these datasets as previously conjectured.

@@

Finally, we examine Figure~\ref{fig:perf_vs_fs_alg}, where we evaluate the
performance distribution of various feature selection algorithms for
two datasets -- NG and S -- and classifier types -- Logistic
Regression and Naive Bayes -- at each stage of feature selection.
This graph shows that our CVL and CVE high recall feature selection
approaches provide strong recall performance at all stages of
feature selection in comparison to other selection methods.
%whose performance varies widely.
%We conjecture the reason for this stems from the strong agreement of
%features provided by the conjunctive voting scheme that helps reduce noise
%during feature selection process.
